Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-04-30 paper.tex
Update figures

\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

@@

\begin{figure}
%  \includegraphics{brain\_classification}
  \includegraphics[scale=0.3]{images/simple_graph}
  \caption{Process graph constructed from an example brain extraction
    script. Every node in the graph is labeled using (1) a process id
    created by our reconstruction, (2) the name of the executable run
    by the process. Processes that read or write temporary files are
    represented with squares; other ones with circles. Plain edges
    represent the process tree (\texttt{fork()} or \texttt{clone()}
    system calls). Dashed edges represent file dependencies: temporary
    files are in yellow and result files are in green.\todo{Add the
      script next to the graph. Remove node colors.}}
  \label{fig:graph-example}
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.3]{images/iterative_modif}
  \caption{iteration of proposed modification.}
  \label{fig:iterations}
\end{figure}

>>>>

\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{listings}
\usepackage{verbatim}

@@

\medskip
\noindent
\begin{minipage}[]{.5\linewidth}
  \centering
  \includegraphics[scale=0.2,width=.4\linewidth]{images/simple_graph}
%  \captionof{figure}{This is a figure caption.} \label{myfig1}
\end{minipage}
\begin{minipage}[]{.3\linewidth}
\small\captionof{algorithm}{sample script of a process graph}\label{sample_script}
%\begin{algorithmic}[1]
%\begin{lstlisting}[frame=single]  % Start your code-block
%
%#!/bin/bash
%
%if [ # !=1 ]
%then
%    echo "usage: 0 <inputimage.nii.gz>"
%    exit 1
%fi
%\end{lstlisting}

{\scriptsize
\begin{verbatim}[frame=single]
#!/bin/bash
if [ # !=1 ]
then
    echo "usage: 0 <inputimage.nii.gz>"
    exit 1
fi
input_image=$1
bet_output="$(basename ${input_image} .nii.gz)_brain.nii.gz"
bet_output_binarized="$(basename ${input_image} .nii.gz)_brain_bin.nii.gz"

bet ${input_image} ${bet_output}
echo "Voxels / Volume in brain mask:"
fslstats ${bet_output} -V
fslmaths ${bet_output} ${bet_output_binarized}
echo "Voxels / Volum in binarized brain mask:"
\rm ${bet_output}
\end{verbatim}
}

%input_image=$1
%bet_output="$(basename ${input_image} .nii.gz)_brain.nii.gz"
%bet_output_binarized="$(basename ${input_image} .nii.gz)_brain_bin.nii.gz"
%
%bet ${input_image} ${bet_output}
%echo "Voxels / Volume in brain mask:"
%fslstats ${bet_output} -V
%fslmaths ${bet_output} ${bet_output_binarized}
%echo "Voxels / Volum in binarized brain mask:"
%\rm ${bet_output}

%  \Procedure{Euclid}{$a,b$}\Comment{The g.c.d. of a and b}
%    \State $r\gets a\bmod b$
%    \While{$r\not=0$}\Comment{We have the answer if r is 0}
%      \State $a\gets b$
%      \State $b\gets r$
%      \State $r\gets a\bmod b$
%    \EndWhile\label{euclidendwhile}
%    \State \textbf{return} $b$\Comment{The gcd is b}
%  \EndProcedure

%\end{algorithmic}
\end{minipage}

\captionof{figure}{Process graph constructed from an example brain extraction
    script. Every node in the graph is labeled using (1) a process id
    created by our reconstruction, (2) the name of the executable run
    by the process. Processes that read or write temporary files are
    represented with squares; other ones with circles. Plain edges
    represent the process tree (\texttt{fork()} or \texttt{clone()}
    system calls). Dashed edges represent file dependencies: temporary
    files are in yellow and result files are in green.} \label{myfig1}

\medskip

@@

\begin{figure}
  \includegraphics[scale=0.6]{images/iterative_modif}
  \caption{iteration of proposed modification.}
  \label{fig:iterations}
\end{figure}
